Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-04 paper/main.tex
incremental approach in section 4

The reduction procedure is given in Algorithm~\ref{alg:single}. Besides
the reduction of acceptance marks, the algorithm also reduces the
number of clauses in acceptance formula if the last argument
$\mathit{reduceC}$ is set to $\true$. In the first step, the procedure
checks whether the input automaton represents the empty language and
if this is the case, it returns the same automaton with acceptance
conditon $\false$ and with all acceptance marks removed. Otherwise it
gradually decreases the number of marks until 0 is reached or the QBF
solver behind the function $\mathit{satisfiable}(\Phi)$ fails to
reduce the number of marks, i.e., it claims unsatisfiability of $\Phi$
or it runs out of resources. In the next step, if $\mathit{reduceC}$
is set to $\true$ then the procedure gradually reduces the number of
clauses. It stops if no equivalent automaton with less clauses is
found or the number of clauses is reduced to one. Note that the
acceptance condition with 0 clauses is $\false$ and this case is
treated at the beginning of the procedure. Finally, if the procedure
succeeds to reduce the number of marks or clauses, if constructs the
modified automaton. Otherwise, it returns the original automaton.
\todo{do sekce o implementaci napsat, ze namisto opakovaneho budovani
  $\Phi_{j,C,K}$ puzivame inkrementalni pristup.}

@@

  \caption{An example illustrating the results of the three basic
    reduction levels: an input automaton and the automata
    obtained by reduction of level 1, level 2, and level 3.}
  \label{fig:example}
\end{figure}

>>>>

The reduction procedure is given in Algorithm~\ref{alg:single}. Besides
the reduction of acceptance marks, the algorithm also reduces the
number of clauses in acceptance formula if the last argument
$\mathit{reduceC}$ is set to $\true$. In the first step, the procedure
checks whether the input automaton represents the empty language and
if this is the case, it returns the same automaton with acceptance
conditon $\false$ and with all acceptance marks removed. Otherwise it
gradually decreases the number of marks until 0 is reached or the QBF
solver behind the function $\mathit{satisfiable}(\Phi)$ fails to
reduce the number of marks, i.e., it claims unsatisfiability of $\Phi$
or it runs out of resources. In the next step, if $\mathit{reduceC}$
is set to $\true$ then the procedure gradually reduces the number of
clauses. It stops if no equivalent automaton with less clauses is
found or the number of clauses is reduced to one. Note that the
acceptance condition with 0 clauses is $\false$ and this case is
treated at the beginning of the procedure. Finally, if the procedure
succeeds to reduce the number of marks or clauses, if constructs the
modified automaton. Otherwise, it returns the original automaton.

Note that the algorithm can be also reformulated to use an incremental
approach instead of building a new formula $\Phi$ in each iteration.
The incremental version of the first \textbf{while} loop builds the formula
$\Phi=\Phi^\mathit{opt}_{j,C,K{-}1}$ only in the first iteration. In
each subsequent iteration, it extends the formula with a condition
saying that one more mark is not used in the automaton, i.e., the mark
is neither on edges, nor in the acceptance formula. For example, if we
want to say that mark $k\in N_K$ is not used in the automaton, we replace
$\Phi$ by
\[
  \Phi~\wedge~\bigwedge_{t\in\delta}\neg n_{t,k}~\wedge\bigwedge_{c\in\{1,2,\ldots C\}}(\neg i_{c,k}\wedge\neg f_{c,k}).
\]
The second \emph{while} can transformed to an incremental version in a
similar way. The advantage of the incremental approach comes from the
fact that some QBF solvers can decide an extended formula faster as
they profit from the information computed when solving the original
formula.

@@

  \caption{An example illustrating the results of the three
    single-level reductions: an input automaton $\mA$ and the automata
    obtained by reducing it with level 1, level 2, and level 3.}
  \label{fig:example}
\end{figure}
